The effects of priming in human computation

### 2014-05-08 docs/draft/pnas1.tex
finish prior work section

Despite the wealth of research investigating the factors influencing 
performance in crowdsourcing, we are unable to find any work showing the 
effects of in-task priming as we have described it.  This is concerning 
because, in the psychology literature, it is well known that priming can have 
powerful effects especially for perceptual tasks related to recognizing 
words, gender, and affect---precisely the types of tasks for which AMT is used
\cite{yuen2011survey, snow2008cheap}.

NOTES ON PRIMING
- when shown an image, a person is better at recognizing the image in a 
	tachistoscope up to 45 min later.\cite{BJOP:BJOP1796}
	* the mechanisms are complex: showing an image of something that had the
		same name also helps recognition, but being presented with a word and
		reading it aloud does not

- priming can be auditory(\cite{BJOP:BJOP1826}) or visual(\cite{BJOP:BJOP1796})

- priming has been detected for words sharing morphemes 
	(reflects vs reflecting) but not for semantically related words that such 
	as held and holding.\cite{BJOP:BJOP1826}
	- suggests stimulus encoding \cite{beller1971priming}\cite{BJOP:BJOP1826}
	\cite{BJOP:BJOP1796} and memory access \cite{beller1971priming} priming 
	effects exist.  Other studies provide definitive evidence that priming
	leads to better application of object knowledge and top-down processes
	\cite{Ghuman17062008}

- existing work suggests that there are separble verbal- and image-based
	semantic systems, as shown through studies of event-related brain 
	potentials in response to high and low imageable words \cite{Swaab200299} 
- priming is an effect whereby previous exposure to a stimulus leads to 
	faster, more accurate responses to similar stimuli \cite{Ghuman17062008}, 
	or lower response thresholds \cite{BJOP:BJOP1826}

@@

Even considering the above explanation, is surprising that 
$\textsc{cult}_{img,x}$ could be strongly influenced to produce more 
cultur-oriented labels, and yet not show increased 
specificity in their use of culture-oriented labels.  Since effects on 
label composition were only appreciable for the first test image 
(see \textbf{Fig. 4}), we also
performed the specificity analysis restricting to labels from the first
test image (see \textbf{Fig. S1}).  But even focusing on the first test image
shows no significant increase in cultural specificity for 
$\textsc{cult}_{img,x}$.  Thus, we observe that orientation of focus and 
label specificity do not necessarily.

>>>>

Despite the wealth of research investigating the factors influencing 
performance in crowdsourcing, we are unable to find any work showing the 
effects of in-task priming as we have described it.  This is concerning 
because, in the psychology literature, it is well known that priming can have 
powerful effects for perceptual tasks related to visual 
recognition of objects \cite{BJOP:BJOP1796}, auditory recognition of words 
\cite{BJOP:BJOP1826}, and the recognition
of gender* and affect*.  These are, of course, precisely the types of tasks 
for which AMT is used \cite{yuen2011survey, snow2008cheap}.

In psychology, priming is a phenomenon whereby previous exposure to a 
stimulus leads to faster, or more accurate responses to similar stimuli 
\cite{Ghuman17062008}, or to lower response thresholds \cite{BJOP:BJOP1826}.
Priming works through various mechanisms.

One mechanism appears to be 
closely related to stimulus encoding \cite{BJOP:BJOP1826}.
Participants are better able to recognize a word in a noisy background when 
primed with a word that shares morphemes 
(e.g. ``reflects'' and ``reflecting'').  However, priming 
with a word that is semantically related, but does not share morphemes doesn't 
help (e.g. ``held'' and ``holding'')\cite{BJOP:BJOP1826}.  Other studies seem
to provide definitive evidence that priming leads to better 
application of object knowledge and top-down processes \cite{Ghuman17062008},
and can also act to facilitate memory access \cite{beller1971priming}.

But the the underlying mechanisms in priming
can be exceedingly subtle \cite{BJOP:BJOP1796}.  As one expects exposing 
participants to an image hels them subsequently recognise that 
image when seen in a tachistoscope.  The researches demonstrated that priming 
using an image that was visually different but of an object having the same 
name also helped participants subsequently identify the image in the 
tachistoscope.  But surprisingly, being presented with related word and 
reading it aloud did not help.  On the basis of these 
results, the researchers suggest the existence of a visual-semantic system,
distinct from the linguistic one \cite{BJOP:BJOP1796}.

Based on the compelling evidence for priming effects in task types often 
employed on AMT, we hypothesize that workers' performance may be impacted
by the very work they have recently performed.  However, we adapt the 
operationalization of priming from one based on speed, accuracy, and 
response threshold, to an algorithmic definition that makes no particular
assumptions about the nature of priming effects.

@@

Another explanation is that food is more so-called \textit{imageable} than 
culture, because although aspects of culture can be depicted in an image,
culture itself cannot.  Studies show that the brain processes high- and 
low-imageable words differently \cite{Swaab200299}, and it would not be 
surprising if the effects of priming on image labeling were modulated by how 
imageable the labels are.

Even with the above explanations, is surprising that 
$\textsc{cult}_{img,x}$ simultaneously could be strongly influenced to 
produce a higher quantity of culture-oriented labels, and yet not a higher
specificity of culture-oriented labels.  Since effects on 
label composition were only appreciable for the first test image 
(see \textbf{Fig. 4}), we also
performed the specificity analysis restricting to labels from the first
test image (see \textbf{Fig. S1}).  But even focusing on the first test image
shows no significant increase in cultural specificity for 
$\textsc{cult}_{img,x}$.  Thus, we observe that orientation of focus and 
label specificity do not necessarily.
